% Define the professional experience section
\sectionTitle{Professional Experience}{\faSuitcase}

\begin{experiences}
  \experience
    {July 2025 - Present} 
    {Software Engineer}{Oracle MADC}{Casablanca, Morocco}
    {} {
      \begin{itemize}
        \item Developed frontend applications using JavaScript and Oracle JET (OJET) framework.
        \item Implemented Backend for Frontend (BFF) patterns to optimize data flow and API integration.
        \item Built responsive user interfaces and integrated GraphQL for efficient data fetching.
        \item Collaborated with backend teams to define API contracts and data structures.
      \end{itemize}
    }
    {JavaScript, Oracle JET (OJET), GraphQL, BFF Pattern, Git, GitLab, Agile, Scrum}
  \experience
    {February 2025 - June 2025} 
    {Backend Intern (FastAPI)}{Oracle MADC}{Casablanca, Morocco}
    {} {
      \begin{itemize}
        \item Contributed to the development of the CSS platform, a cloud monitoring system based on microservices.
        \item Implemented new REST API endpoints and features using FastAPI and Python.
        \item Wrote and maintained unit tests, and fixed bugs to ensure system stability and reliability.
        \item Collaborated with a multidisciplinary team following Agile methodology with daily Scrum meetings.
        \item Used Git and GitLab for version control and continuous integration workflows.
      \end{itemize}
    }
    {Python, FastAPI, JavaScript, Git, GitLab, Agile, Scrum, Microservices, Unit Testing}
  \emptySeparator
\end{experiences}